Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-18 ieee_paper.tex
removing some todo

\section{Experimental Validation}
\label{sec:expe}
In this section, we describe a series of numerical experiments to
confirm the performance predictions of Section~\ref{sec:model}. To
better understand our results, we first perform some bandwidth
measurements, followed by the actual SpMV computations. All the codes
are compiled with the Intel C Compiler version xxx\todo{gordon?} and
-O3 optimization. The MIC codes use the IMCI instructions exposed by
the compiler through intrinsics.

@@

  \caption{On MIC with 240 threads, 64-byte memory
    alignment. Bandwidth performance under idealized
    conditions as a function of matrix row size.  Entries with "cpp"
    denote cases where coding was performed without MIC vector
    instructions. \todo{legend}  \todo{Can we label the x-axis "number of floats" or
      "size in MB"?}\todo{Can we use the same symbols in both charts?}
    \todo{Can we change the color scheme? in (a), I do not see the
      difference between "read\_cpp" and "read/write cpp"} }
  \label{fig:bandwidth}
  \label{fig:band_rw_MIC}
\end{figure}

>>>>

\section{Experimental Validation}
\label{sec:expe}
In this section, we describe a series of numerical experiments to
confirm the performance predictions of Section~\ref{sec:model}. To
better understand our results, we first perform some bandwidth
measurements, followed by the actual SpMV computations. All the codes
are compiled with the Intel C Compiler version 13 and
-O3 optimization. The MIC codes use the IMCI instructions exposed by
the compiler through intrinsics.

@@

  \caption{On MIC with 240 threads, 64-byte memory
    alignment. Bandwidth performance under idealized
    conditions as a function of matrix row size.  Entries with "cpp"
    denote cases where coding was performed without MIC vector
    instructions. \todo{legend} }
  \label{fig:bandwidth}
  \label{fig:band_rw_MIC}
\end{figure}
